To-Do List

### 2016-01-19 Rmd/to-do.Rmd
Created new carbon layers

# make an html table
# http://r-norberg.blogspot.com/2013/06/generating-tables-using-pander-knitr.html
tabl <- cbind(
  "Item" = c("Plausible Scenario", 
             "Gridded yields",
             "Gridded yields",
             "Upgrade soils", 
             "Filter terrain", 
             "Biodiversity impacts", 
             "Impacts weighting (per Tim)", 
             "Work in economics", 
             "Explore econ versus enviro goals", 
             "Better cropland map, yield estimates"), 
  "Notes" = c("Single production to follow (Alastair)", 
              "Exact method for variability and production zones, including inability to reach potential yields", 
              "Run with improved soils maps", 
              "With ILUA database (and Nate's help)", 
              "Removable unfarmable areas, add new supporting logic", 
              "Habitat rarity/threatenedness", 
              "Weight carbon and biodiversity equally", 
              "Estimate profitability per pixel. Either input modification or code modification", 
              "See where map overlaps are greatest, most divergent", 
              "Upgrade all maps to SERVIR landcover, and rebase yield estimates on that"),
  "Doing" = c("D", "D", "U", "U", "D", "D", "D", "L", "D", "D")
)
print(xtable::xtable(tabl), align = rep("c", dim(table)[2] + 1), type = "html", 
      include.rownames = FALSE)
```

>>>>

# make an html table
# http://r-norberg.blogspot.com/2013/06/generating-tables-using-pander-knitr.html
tabl <- cbind(
  "Item" = c("Plausible Scenario", 
             "Gridded yields",
             "Gridded yields",
             "Upgrade soils", 
             "Filter terrain", 
             "Biodiversity impacts", 
             "Impacts weighting (per Tim)", 
             "Work in economics", 
             "Explore econ versus enviro goals", 
             "Better cropland map, yield estimates", 
             "Updated carbon layers"), 
  "Notes" = c("Single production to follow (Alastair)", 
              "Exact method for variability and production zones, including inability to reach potential yields", 
              "Run with improved soils maps", 
              "With ILUA database (and Nate's help)", 
              "Removable unfarmable areas, add new supporting logic", 
              "Habitat rarity/threatenedness", 
              "Weight carbon and biodiversity equally", 
              "Estimate profitability per pixel. Either input modification or code modification", 
              "See where map overlaps are greatest, most divergent", 
              "Upgrade all maps to SERVIR landcover, and rebase yield estimates on that", "Baccini vegetation carbon + ISRIC grids"),
  "Doing" = c("D", "D", "U", "U", "D", "D", "D", "L", "D", "D", "F")
)
print(xtable::xtable(tabl), align = rep("c", dim(table)[2] + 1), type = "html", 
      include.rownames = FALSE)
```
